---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# farspackage

The goal of farspackage was to develop and upload a package for Week #4 of the 
Coursera course Building R Packages (part of the Mastering Software Development
in R Specialization).

The *farspackage* contains various functions to read from file, summarize, and 
map data from the US National Highway Traffic Safety Administration's 
[Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars)

This data encompasses the yearly data regarding fatal injuries suffered in 
motor vehicle traffic crashes.

## Installation

This package can be installed and loaded with:

```{r eval=FALSE}
devtools::install_github("ilikefishes/farspackage")
library(farspackage)
```

For more information on functionality and usage, please view the included
vignette or documentation.
