---
title: "farspackage Information"
author: "Devan Sperlie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{farspackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r echo=FALSE, warning=FALSE}
suppressMessages(library(farspackage))
suppressMessages(library(dplyr))
suppressMessages(library(maps))
```


### Package Description

The *farspackage* contains various functions to read from file, summarize, and 
map data from the US National Highway Traffic Safety Administration's 
[Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars)

### farspackage Functions

#### make_filename()

This function will create a file name using the **year** argument that
will be compatible for use in the other farspackage functions. If a string in
integer format is passed, it will be converted to an integer to avoid NA's by
coercion.

```{r}
make_filename(2014)
```

#### fars_read()

This function will create a tibble data.frame based on a FARS filename passed
as the **filename** argument.  If the filename does not exist, an error 
will be thrown advising it does not exist.

```{r}
fars_read("accident_2014.csv.bz2")
```

#### fars_read_years()
This function will return a list of month and years for all rows that are
present in a FARS data set. The **years** argument can be a vector or list of year in
integer format. An error will be thrown if a year and corresponding file does 
not exist.
```{r}
fars_read_years(2014)
```

#### fars_summarize_years()

This function will return a summary of total number of fatalities per month
and year. The **years** argument can be a vector or list of year(s) in integer format.

```{r}
fars_summarize_years(2014)
```

#### fars_map_state()

This function will create a map of fatal accidents based on the **state.num**
and **year** arguments. An error will be thrown if an invalid state number
is provided. A message will also be printed if there are zero fatalities to 
map.

```{r}
fars_map_state(1,2014)
```

